\Title

### 2020-03-02 manuscript/manuscript.tex
Define parameters units on tables

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \GroundSourceBellowDataConstantDepthDepth
              & \GroundBlockMedianSourcesConstantDepthDepth
              & \GroundGridSourcesConstantDepthDepth \\
        Spacing & -
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataRelativeDepthDepth
              & \GroundBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataVariableDepthDepth
              & \GroundBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \AirborneSourceBellowDataConstantDepthDepth
              & \AirborneBlockMedianSourcesConstantDepthDepth
              & \AirborneGridSourcesConstantDepthDepth \\
        Spacing & -
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataRelativeDepthDepth
              & \AirborneBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataVariableDepthDepth
              & \AirborneBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}

>>>>

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
                   & \GroundBlockMedianSourcesConstantDepthDepth
                   & \GroundGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesConstantDepthSpacing
                     & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
                   & \GroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
                   & \GroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
                   & \AirborneBlockMedianSourcesConstantDepthDepth
                   & \AirborneGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesConstantDepthSpacing
                     & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
                   & \AirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesRelativeDepthSpacing
                     & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
                   & \AirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}
